---
title: "Assignment 3 ex2"
author: "Minh Nhat Tran"
date: "03/10/2019"
output:
  pdf_document: default
  html_document: default
---

# Exercise 2
### Input

```{r}
rm(list=ls())
prem<-5000
premfeerate<-c(0.45,rep(0.01,9))
buysellmarginrate<-0.005
unitfundrate<-0.1
nonunitfundrate<-0.08
assetfee<-0.003

```


### Mortality Rates
```{r}
year<-c(1:10)
x<-c()
x<-year+29
x
qd<-c(0.00043,0.00042,0.00041,0.00040,0.00041,0.00042,0.00043,0.00045,0.00049,0.00053)
qw<-c(0.25,0.2,0.175,rep(0.15,6),1)

aqd<-qd*(1-0.5*qw)
aqw<-qw*(1-0.5*qd)
al<-c()
add<-c()
adw<-c()
al[1]<-100000

for(i in 1:10){
  add[i]=aqd[i]*al[i]
  adw[i]=aqw[i]*al[i]
  al[i+1]=al[i]-add[i]-adw[i]
  }
```



### Unit fund
#### Premium
```{r}
investedprem.BoY<-rep(prem,10)*(1-premfeerate)*(1-buysellmarginrate)
```


#### Value of Units
```{r}
valueofunits.EoY<-c()
valueofunits.EoY[1]<-investedprem.BoY[1]*(1+unitfundrate)*(1-assetfee)

for(i in 2:10){valueofunits.EoY[i]=(investedprem.BoY[i]+valueofunits.EoY[i-1])*(1+unitfundrate)*(1-assetfee)

}
valueofunits.EoY[1:10]
```

#### Expected amounts per initial policy
```{r}
e_investedprem.BoY<-c()
e_investedprem.BoY[1:10]<-investedprem.BoY[1:10]*al[1:10]/al[1]

e_valueofunits.EoY<-c()
e_valueofunits.EoY[1:10]<-valueofunits.EoY*al[2:11]/al[1]

e_interest<-c()
e_interest[1]<-e_investedprem.BoY[1]*unitfundrate
e_interest[2:10]<-(e_investedprem.BoY[2:10]+e_valueofunits.EoY[1:9])*unitfundrate
changeinpv<-c()
changeinpv[1]<-e_valueofunits.EoY[1]
changeinpv[2:10]<-e_valueofunits.EoY[2:10]-e_valueofunits.EoY[1:9]
changeinpv


transfer<-e_investedprem.BoY[1:10]+e_interest-changeinpv

tableunitfund<-cbind(year,e_investedprem.BoY[1:10],e_interest,e_valueofunits.EoY,transfer)
colnames(tableunitfund)<-c("Year","Inv.Premium BOY","Interest EOY","Value.Unit EOY","Transfer EOY")
tableunitfund
```

### Non-Unit Fund
```{r}

premfee.BoY<-prem*premfeerate

buysellmargin.BoY<-prem*(1-premfeerate)*buysellmarginrate

expense.BoY<-c()
expense.BoY[1]<-0.45*prem+58
expense.BoY[2:10]<-58*(1+0.2)^(year[2:10]-1)

bft.EoY<-valueofunits.EoY

e_premfee.BoY<-premfee.BoY*al[1:10]/al[1]

e_buysellmargin.BoY<-buysellmargin.BoY*al[1:10]/al[1]

e_expense.BoY<-expense.BoY*al[1:10]/al[1]

e_nonunitfundinterest.EoY<-(e_premfee.BoY+e_buysellmargin.BoY-e_expense.BoY)*nonunitfundrate

deathbft.EoY<-bft.EoY*add/al[1]
surrbft.EoY<-bft.EoY*adw/al[1]

nonunitfundtransfer<-e_premfee.BoY+e_buysellmargin.BoY-e_expense.BoY+e_nonunitfundinterest.EoY+transfer-deathbft.EoY-surrbft.EoY

tablenonunitfund<-cbind(year,e_premfee.BoY,e_buysellmargin.BoY,e_expense.BoY,e_nonunitfundinterest.EoY,transfer,deathbft.EoY,surrbft.EoY,nonunitfundtransfer)
colnames(tablenonunitfund)<-c("Year","Prem-based fees BOY","B-S Margin BOY","Expenses BOY","Interest EOY","Transfer UnitFund EOY","Death Bft EOY","Surr Bft EOY","Transfer")
tablenonunitfund
```

# Part a_ Profit Signature and EPV of transfer
### Profit signature
```{r}
nonunitfundtransfer
```
### Expected value of transfer
```{r}
npvprofit<-function(a){sum(a*(1+0.125)^-(year))}
npvprofit(nonunitfundtransfer)
npvprofit(nonunitfundtransfer)/prem    #profit margin
npvprofit1<-function(i){sum(nonunitfundtransfer*(1+i)^-(year))}
```
### IRR
```{r}
uniroot<-uniroot(npvprofit1,c(0,1))
uniroot
uniroot$root[[1]]
```
 


# Part b_Zeroising balance

```{r}
nonunitfundtransfer[10]
policyvalue<-valueofunits.EoY



pv<-function(n){e_valueofunits.EoY[9]<-n*al[10]/al[1]
e_interest[10]<-(e_investedprem.BoY[10]+e_valueofunits.EoY[9])*unitfundrate
changeinpv[9:10]<-e_valueofunits.EoY[9:10]-e_valueofunits.EoY[8:9]
transfer[9:10]<-e_investedprem.BoY[9:10]+e_interest[9:10]-changeinpv[9:10]
nonunitfundtransfer[9:10]<-e_premfee.BoY[9:10]+e_buysellmargin.BoY[9:10]-e_expense.BoY[9:10]+e_nonunitfundinterest.EoY[9:10]+transfer[9:10]-deathbft.EoY[9:10]-surrbft.EoY[9:10]
nonunitfundtransfer[10]}

uniroot<-uniroot(pv,c(1,100000))
uniroot

policyvalue[9]<-uniroot$root[[1]]
policyvalue[9]-valueofunits.EoY[9]
```

### Changes resulted from the change in policy value in Y9
```{r}

e_valueofunits.EoY[1:10]<-policyvalue*al[2:11]/al[1]
e_interest[2:10]<-(e_investedprem.BoY[2:10]+e_valueofunits.EoY[1:9])*unitfundrate
changeinpv[2:10]<-e_valueofunits.EoY[2:10]-e_valueofunits.EoY[1:9]
transfer<-e_investedprem.BoY[1:10]+e_interest-changeinpv
tableunitfund<-cbind(year,e_investedprem.BoY[1:10],e_interest,e_valueofunits.EoY,transfer)
colnames(tableunitfund)<-c("Year","Inv.Premium BOY","Interest EOY","Value.Unit EOY","Transfer EOY")
tableunitfund
zerononunitfundtransfer<-e_premfee.BoY+e_buysellmargin.BoY-e_expense.BoY+e_nonunitfundinterest.EoY+transfer-deathbft.EoY-surrbft.EoY

tablenonunitfund<-cbind(year,e_premfee.BoY,e_buysellmargin.BoY,e_expense.BoY,e_nonunitfundinterest.EoY,transfer,deathbft.EoY,surrbft.EoY,zerononunitfundtransfer)
colnames(tablenonunitfund)<-c("Year","Prem-based fees BOY","B-S Margin BOY","Expenses BOY","Interest EOY","Transfer UnitFund EOY","Death Bft EOY","Surr Bft EOY","Transfer")
tablenonunitfund
```
 Check zero transfer in year 10
```{r}
 floor(zerononunitfundtransfer[10])

```

# Part c_EPV of transfer after zeroising
```{r}
npvprofit(zerononunitfundtransfer)
npvprofit(zerononunitfundtransfer)-npvprofit(nonunitfundtransfer)
```
 The expected present value of transfers decreases due to the difference between the interest rate and the risk discount rate.
  
 When we want the transfer in year 10 to be 0 and increase the policy value in year 9, the transfer in year 9 will decrease, meaning higher reserves defer the emergence of profit. While the holding of more reserve will result in an increase in interest earned of 10% in the unit fund, the valuation basis for interest rate is higher, leading to a decrease in net present value.



