---
title: "Question 3"
author: "Minh Nhat Tran"
date: "22/08/2019"
output: html_document
---
**Question 3**
a)
Calculate Theresa's commission following discounted cashflow approach, given that her commision schedule is subjected to the same pattern as Bill's repayments. We can use her annual commission times the annuity factor calculated in Q1 
```{r}
i=0.035
v=(1+i)^-1
pmt=32622.8
annuity=(1-v^30)/i
Q3a<-1000*annuity
Q3a
```
b)
The effective interest rate that the bank requires on his funds is actually lower than the rate given to public as part of the profit is shared by the agent's commission.

c)
```{r}
f3<-function(i){(pmt-1000)*(1-(1+i)^(-30))/i-600000}
uni3<-uniroot(f3,interval=c(0.01,5))
Q3c<-uni3$root[[1]]
Q3c
```
We assume that Theresa's commusion is valued at the same rate as the repayments. Hence, for each repayment that Scott makes, an extra $1,000 is taken out. We then can evaluate the fomula for the annuity, in which we can calculate the discounted rate using uniroot function.

d)
```{r}
i1<-Q3c
f3d<-function(pmt1){pmt1*(1-(1+i1)^-30)/i1-600000}
uni3d<-uniroot(f3d,interval=c(0,100000))
Q3d<-uni3d$root[[1]]
Q3d

```
