---
title: "Question 2"
author: "Minh Nhat Tran"
date: "22/08/2019"
output: html_document
---
**Question 2**
  a)
  Without the offset account taken into consideration, Scott's repayment amount should be the same as that of Bill since both of them take in a loan of equal amount, and on the same term.
The annual repayment from Scott is $32,622.8

  b)
  Given annual payment amount, now with an addition payment made from the offset account, we can calculate the number of year taken for Scott to extinguish his loan. 
```{r}
pmt=32622.8
f2<-function(n){(pmt+100000*0.035)*(1-v^n)/i+100000*(1+i)^-n-600000}
uni2<-uniroot(f2,interval=c(0,30))
uni2
Q2<-ceiling(uni2[[1]])
Q2
```
At the period 22, his loan outstanding is slightly above the amount in his offset account, which means his loan can be paid in a period later, period 23, when he pays that difference, plus any difference in interest arised.

The final payment can be calculated by calculating the loan outstanding in period 22,plus the interest from the loan, minus the interest from his offset account and the amount in his offset account.
(\(L_t=L_0 - \sum_{t=1}^{n}(1+i)^{t-s}.R\)
```{r}
Lt<-600000*(1+i)^22-((pmt+100000*0.035)*(1-v^22)/i)*(1+i)^22
```

```{r}
Lt*1.035-0.035*100000-100000
```
The difference mentioned above is the last payment for Scott to extinguish his loan. The amount is $11484.86
